Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-02-13 paper/rei.tex

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{Tanh chains with plik\_full\_TTTEEE for the high-l likelihood. [remove PC zmax curve; add PC filtered version]
}
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_taugtz_tanh_highz_direct_vs_kde_vs_gaussian_dz_auto_zre_prior_6p1.pdf}
\caption{The 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ for the two-step model, which allows for high-redshift ionization up to $\zmax =30$. note that a physical model with $\tau(15, \zmax) = 0.02$ is still allowed at the 95\% C.L. whereas the Planck FlexKnot analysis would have ruled it out with their $\tau(15, \zmax) < 0.007$ 95\% upper limit. [add not PC filtered version]
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}

>>>>

\begin{figure}[ht]
\includegraphics[width=0.5\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Cumulative optical depth for the tanh model from direct MCMC chains, KDE chians and Gaussian likelihood chains. 
}
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{plots/pl18_taugtz_tanh_highz_direct_vs_kde_vs_gaussian_dz_auto_zre_prior_6p1.pdf}
\caption{The 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ for the two-step model, which allows for high-redshift ionization up to $\zmax =30$. note that a physical model with $\tau(15, \zmax) = 0.02$ is still allowed at the 95\% C.L. whereas the Planck FlexKnot analysis would have ruled it out with their $\tau(15, \zmax) < 0.007$ 95\% upper limit. [add not PC filtered version]
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}

@@
